%------------------------
% Resume in Latex
% Author : Harshibar
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO EBSERIES
% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

% \newcommand{\resumeProjectHeading}[2]{
%     \item
%     \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%       #1 & {\color{dark-grey}} \\
%     \end{tabular*}\vspace{-4pt}
% }
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey} #2} \\  % Include #2 for the date range
    \end{tabular*}\vspace{-4pt}
}


% \newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
% \newcommand{\resumeSubItem}[1]{\hspace{2em} \resumeItem{#1}\vspace{-4pt}}
% \newcommand{\resumeSubItem}[1]{
%   \item[] \hspace{2em} \small{#1 \vspace{-1pt}}
% }
\newcommand{\resumeSubItem}[1]{
  \begin{itemize}
    \item \small{#1 \vspace{-1pt}}
  \end{itemize}
}


\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\footskip}{5pt}
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Joe (Yung-Hung) Huang} \\ \vspace{5pt}    
    \hspace{1pt} \faEnvelope \hspace{2pt} \texttt{\href{mailto:yunghunghuang984@gmail.com}{yunghunghuang984@gmail.com}} \hspace{1pt} $|$
    \hspace{1pt} \faGithub \hspace{2pt} \texttt{\href{https://github.com/blackdesert575}{blackdesert575}} \hspace{1pt} $|$
    %\hspace{1pt} \faYoutube \hspace{2pt} \texttt{harshibar} \hspace{1pt} $|$
    \hspace{1pt} \faMapMarker* \hspace{2pt}\texttt{Taiwan (R.O.C) Taipei}
    \\ \vspace{-3pt}
\end{center}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

\resumeSubheading
  {System / DevOps Engineer}{Jun. 2025 -- Present}
  {Logic Solutions Inc.}{}
  \resumeItemListStart
    \resumeItem{Designed, implemented, and maintained \textbf{scalable, reliable, and observable product system architectures} across \textbf{AWS and on-premise / hybrid environments}.}
    \resumeItem{Operated and maintained \textbf{AWS cloud infrastructure} (VPC, EC2, RDS, Load Balancers, ...etc), ensuring system stability, security, and performance for production workloads.}
    \resumeItem{Automated infrastructure provisioning and system initialization using \textbf{Infrastructure as Code (IaC)}, leveraging \textbf{Terraform, Terragrunt, Atlantis, Packer, and Ansible} to build reusable AMIs and standardized service stacks.}
    \resumeItem{Built and maintained \textbf{CI/CD pipelines} using \textbf{Jenkins and GitLab}, including authoring and maintaining \textbf{Groovy scripts} to support build, deployment, and operational workflows.}
    \resumeItem{Performed \textbf{root cause analysis and troubleshooting} for service errors, performance issues, and system anomalies using \textbf{Linux CLI tools, metrics, and logs} across cloud and on-premise environments.}
    \resumeItem{Extended system \textbf{observability and reliability} by integrating \textbf{Prometheus, Grafana, Alertmanager, Consul, and custom exporters}, enabling proactive monitoring and incident response.}
    \resumeItem{Supported deployment, upgrades, and operational maintenance of product systems deployed in \textbf{customer environments}, including \textbf{AWS, Cloudflare, and hybrid on-premise setups}.}
    \resumeItem{Reviewed an existing \textbf{GitOps-based Kubernetes architecture} on \textbf{AWS EKS} and, based on \textbf{product scale, operational cost, and system maturity}, led the \textbf{decommissioning of EKS node groups} and the retirement of related subsystems (\textbf{Istio, Karpenter, Argo CD}, etc.) to reduce operational overhead and technical debt.}
  \resumeItemListEnd

  \resumeSubheading
  {System/Site Reliability Engineering (SRE)/DevOps Engineering}{Nov. 2023 -- Dec. 2024}
  {Mending Technology CO., LTD.}{}  
  \resumeItemListStart
    \resumeItem{Supported a \textbf{cryptocurrency exchange platform} on AWS and on-premise infrastructure, focusing on making large-scale systems more controllable through \textbf{environment isolation}, \textbf{infrastructure automation}, and \textbf{reliability-oriented practices} across development, test, staging, and production environments.}
      \resumeSubItem{Built a Docker container-based \textbf{toolbox} for \textbf{troubleshooting and automation development} across \textbf{AWS and on-premise environments}, enabling team members to quickly \textbf{set up standardized workflows}.}
      \resumeSubItem{Worked with the team to \textbf{build an on-premise development environment} using \textbf{VMware vSphere, Kubernetes (kubeadm), and MetalLB}, reducing dependency on a shared AWS environment and improving developer productivity and environment isolation.}
      \resumeSubItem{Implemented \textbf{Infrastructure as Code (IaC)} using \textbf{Pulumi (Python) and Ansible} to automate infrastructure changes in the \textbf{production environment} and provision a \textbf{staging environment} for QA, SRE, and DevOps teams.}
      \resumeSubItem{Participated in \textbf{SRE/DevOps roadmap discussions} focused on improving system controllability, including Docker image hardening, observability enhancements, and automation of incident response workflows, aiming to reduce reliance on individual experience when diagnosing production issues.}
      \resumeSubItem{Overall, my work focused on \textbf{turning complex cryptocurrency exchange infrastructure} into systems that are \textbf{easier to reason about, operate, and recover from failures}.}
  \resumeItemListEnd

  \resumeSubheading
  {Site Reliability Engineering (SRE)/DevOps/Cloud engineering}{Nov. 2021 -- April. 2023}
  {CloudRock Technology Co., Ltd}{}  
  \resumeItemListStart
    \resumeItem{Worked from a  Cloud to SRE/DevOps engineer in a consulting environment, supporting \textbf{multiple client systems} (e.g., social/chat applications, payment systems, sports data platforms, and live streaming services) by designing, migrating, and operating systems across \textbf{AWS, GCP, Alibaba Cloud, and Cloudflare}.}
      \resumeSubItem{Designed and evolved \textbf{CNCF-aligned system architectures} by introducing \textbf{Docker containerization, Kubernetes orchestration, and Ingress-Nginx + cert-manager} across different project phases.}
      \resumeSubItem{Built and operated cloud-native systems using managed services (\textbf{EC2, EKS, GKE, ELB, RDS}) and self-hosted middleware (\textbf{Nacos, RocketMQ, Redis}), balancing cost, performance, and operational complexity.}
      \resumeSubItem{Maintained and troubleshot \textbf{multiple Kubernetes clusters} for client environments, providing performance tuning, deployment optimization, and incident-level support.}
      \resumeSubItem{Built and maintained \textbf{GitLab CI and Jenkins pipelines} for client projects, including optimization of \textbf{.gitlab-ci.yml} and Bash-based GitLab Runner workflows, reducing cross-region CI execution latency and improving pipeline stability.}
    \resumeItem{Developed a \textbf{Python-based automation project (boce-crawler)} to collect external network metrics and provide a reliable monitoring data source.}
      \resumeSubItem{Implemented a \textbf{scheduled data collection pipeline} using Python and crontab to extract metrics from third-party websites, transform the data, and load it into \textbf{MariaDB} as a \textbf{Grafana data source}.}
      \resumeSubItem{Designed a temporary \textbf{fallback monitoring solution} to mitigate data loss caused by instability of a third-party monitoring API, ensuring \textbf{continuous metric availability} for approximately three months until a replacement service was adopted.}
  \resumeItemListEnd

\resumeSubheading
  {IoT Bootcamp (Full-Stack \& System Fundamentals Training)}{Jan. 2021 -- May. 2021}
  {Industrial Technology Research Institute (ITRI)}{}
  \resumeItemListStart
    \resumeItem{Completed an intensive hands-on training program covering \textbf{web development fundamentals, system programming, Linux environments, networking basics, and IoT system integration}.}
    \resumeSubItem{Implemented basic \textbf{front-end web pages using pure HTML, CSS, and JavaScript}, followed by backend development with \textbf{PHP and MySQL} for data persistence and integration.}
    \resumeSubItem{Built a local \textbf{Linux (Ubuntu) development environment using VirtualBox} and practiced foundational \textbf{Linux system programming concepts}, including process management, file systems, and networking fundamentals.}
    \resumeSubItem{Acted as a technical lead during team-based projects by introducing \textbf{Git and GitLab} for source code management, enabling collaborative development and version control workflows.}
    \resumeSubItem{Led the implementation of an \textbf{IoT monitoring system (IndoorAirBox)} using \textbf{Raspberry Pi and ESP8266}, focusing on temperature and humidity data collection with available course resources.}
  \resumeItemListEnd


  \resumeSubHeadingListEnd  

%-----------PROJECTS-----------

\section{PROJECTS}

    \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{homelab}} {Jun. 2023 -- Present}
        \resumeItemListStart
          \resumeItem{From \textbf{CNCF's Definition} , trying to build \textbf{lightweight Hybrid Cloud infrastructure} for \textbf{enhancement of personal tech stacks, building personal apps...etc}}
          \resumeItem{\textbf{Tech Stack}: Python, Bash, Golang, Rust, JavaScript/TypeScript, HTML5, CSS, Cloudflare, AWS, Linux ,Proxmox Virtual Environment, Docker, k3s/k0s cluster(Lightweight Kubernetes), *-exporters, Prometheus, Grafana, ELK stack, Terrform, Ansible, Github Actions, Jenkins Container Registry, service mesh (linkerd), MongoDB, PostgreSQL, MySQL, InfluxDB, ... etc}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

    \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{resume}} {Mar. 2023 -- Present}
        \resumeItemListStart
          \resumeItem{Building \textbf{a online CV website} based on \textbf{LaTeX} to record my experience, projects, education, skills.}
          \resumeItem{Render a CV file via \textbf{single HTML-CSS-JavaScript transform from PDF Source with pdf2htmlEX} or access \textbf{PDF file directly via built-in PDF viewer of browsers(Google Chrome, Brave, Firefox, Safari...etc)}}
          \resumeItem{Learning concepts of \textbf{Serverless services via Cloudflare Workers and Pages}}
          \resumeItem{Development and Deployment CI/CD pipelines with \textbf{Bash, Docker, GitHub, Cloudflare Pages} to make \textbf{Proof of concept.}}
          \resumeItem{\textbf{Tech Stack}: LaTeX, pdf2htmlEX, Bash, JavaScript/TypeScript, node.js, React, Next.js, GNU Make, Github, Linux, Docker, Nginx, Cloudflare Workers and Pages}
        \resumeItemListEnd          
    \resumeSubHeadingListEnd

    \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{setup devops environment}} {Dec. 2022 -- Present}
        \resumeItemListStart
          \resumeItem{Building \textbf{a personal notes website} based on \textbf{Material for MkDocs} to render Markdown files to web pages.}
          \resumeItem{\textbf{Tech Stack}: Python, Bash, Yaml, Markdown, Github, GitHub Actions, Linux, Docker, Nginx, Cloudflare}
        \resumeItemListEnd          
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section {EDUCATION}
\resumeSubHeadingListStart
\resumeSubheading
  {National Dong Hwa University}{Sep. 2016 -- Jan. 2019}
  {Master of Science in Materials Science and Engineering}{Shoufeng, Hualien}
    \resumeItemListStart
  \resumeItem {\textbf{Thesis}: Ultrafast Pump-probe Transient Absorption Spectroscopy of Layer-controllable Molybdenum Disulfide Films}
    \resumeItem 
        {\textbf{Research}: Semiconductor Materials }
    \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
  {National Dong Hwa University}{Sep. 2012 -- Jun. 2016}
  {Bachelor of Science in Materials Science and Engineering}{Shoufeng, Hualien}
    \resumeItemListStart
    \resumeItem {Program of Advanced Materials}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Languages}{: Mandarin (native), English (professional working proficiency)}\vspace{2pt} \\
     \textbf{Programming Languages}{: Python(proficient), Bash(competence), SQL(competence), Golang(beginner), Rust(beginner)}\vspace{2pt} \\
     \textbf{Version Control}{: git} \\
     \textbf{Frameworks}{: Django, FastAPI, Selenium, pandas, SQLAlchemy} \\
     \textbf{Operating system}{: Linux(proficient), macOS(beginner), Windows(beginner)}\\
     \textbf{Continuous Integration(CI) \& Continuous Delivery(CD)}{:GitLab Runner, Github Actions, Jenkins, Tekton Pipelines, Argo CD} \\
     \textbf{Streaming \& Messaging}{: Apache RocketMQ, RabbitMQ} \\
     \textbf{Scheduling \& Orchestration}{: Kubernetes(EKS, GKE, ACK, k0s...etc), KEDA} \\
     \textbf{Service Proxy}{: NGINX, HAProxy, MetalLB, Envoy} \\
     \textbf{Service Mesh}{: Consul} \\
     \textbf{Coordination \& Service Discovery}{: Apache Zookeeper, Nacos, Netflix Eureka} \\
     \textbf{Container Registry}{: Harbor} \\
     \textbf{Automation \& Configuration}{: Ansible, Atlantis, Terraform, Terragrunt, Pulumi, Ansible} \\
     \textbf{Cloud Providers}{: AWS, Google Cloud, Alibaba Cloud, Cloudflare} \\
     \textbf{Certification}{: AWS Certified Solutions Architect Associate, AWS Certified Cloud Practitioner}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}